\documentclass[main]{subfiles} 
\graphicspath{{img/}}


\begin{document}


\subsection*{Aim}

The aim of this project is to build a platform from which the current prices, availability and origin of products offered at the swiss retailer Migros can be displayed.

Efficiently obtaining the data, ordering and storing it in a (computationally) efficient manner will be a major focus of this project. 
The platform should be able to quickly give information on prices, 
availability and stock levels of a selected product based on the  ZIP code (for example). 
This platform will also be used for further analysis in the project for the course "Advanced Data Analysis"

% Using the knowledge obtained from the course "Advanced Data Analysis" we mainly aim to produce the backend 



\subsection*{Data}
The data will be obtained mainly by scraping the website of Migros.
We aim to build a small database which is kept up-to-date regularly so that a (short term) time series can be constructed.
Within the scope of this project is also the maintenance of the data so that the project in "Advanced Data Analysis" can focus on just that: analysing the scraped data. 
Depending on how well-maintained the API of Migros is and whether we are granted access, the API will be consulted as well.

Due to swiss regulation Migros is obliged to declare the place of origin, sometimes including a unique identification of the producer, of their animal products. 
We especially want to obtain this data in order to advance the project in "Advanced Data Analysis".


\end{document}